The \dealii Library, Version 9.2

### 2020-05-13 9.2/paper.tex
Add a couple of comments.
Update a comment.

The major changes of this release are:
%
\begin{itemize}
\item xy \todo[inline]{Update once we have the subsections in Section 2;
  provide cross-references to each of these subsections}
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}), 
\end{itemize}
%
The major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item x \todo[inline]{Wolfgang to write about complex-valued output}
\item y \todo[inline]{Timo to write about problems and fixes for
  computations with more than $2^{32}$ unknowns}
\item z \todo[inline]{What else?}
\end{itemize}
%
In addition to these changes, the changelog lists more than 200 other
features and bugfixes.

@@

Many of the \dealii{} tutorial programs were substantially revised as
part of this release. In particular, we have converted many places
that now allow for simpler code through the use of C++11 features such
as range-based for loops and lambda functions.

In addition, there are seven new tutorial programs:
\begin{itemize}
\item \texttt{step-47}
\todo[inline]{Zhuoran to write}
\item \texttt{step-50}
\todo[inline]{Timo/Conrad/... to write}
\item \texttt{step-58}
\todo[inline]{Wolfgang to write}  
\item \texttt{step-65}
\todo[inline]{Martin to write}  
\item \texttt{step-67}
\todo[inline]{Martin to write}  
\item \texttt{step-69}
\todo[inline]{Matthias/Ignacio to write}  
\item \texttt{step-70}
  \todo[inline]{Also need to update announce and announce-short if this
    makes it into the release.}
\end{itemize}

>>>>

The major changes of this release are:
%
\begin{itemize}
\item xy \todo[inline]{Update once we have the subsections in Section 2;
  provide cross-references to each of these subsections}
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}), 
\end{itemize}
%
The major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item x \todo[inline]{Wolfgang to write about complex-valued output}
\item y \todo[inline]{Timo to write about problems and fixes for
  computations with more than $2^{32}$ unknowns}
\item z \todo[inline]{What else? Maybe mention the updated step-12?}
\end{itemize}
%
In addition to these changes, the changelog lists more than 200 other
features and bugfixes.

@@

Many of the \dealii{} tutorial programs were revised in a variety of
ways as part of this release. A particular example is that we have
converted a number of programs to use range-based for loops (a C++11
feature) for loops over a range of integer indices, given that the
range-based way of writing loops seems to be the idiomatic approach
these days.

In addition, there are a number of new tutorial programs:
\begin{itemize}
\item \texttt{step-47}
\todo[inline]{Zhuoran to write}
\item \texttt{step-50}
\todo[inline]{Timo/Conrad/... to write}
\item \texttt{step-58}
\todo[inline]{Wolfgang to write}  
\item \texttt{step-65}
\todo[inline]{Martin to write}  
\item \texttt{step-67}
\todo[inline]{Martin to write}  
\item \texttt{step-69}
\todo[inline]{Matthias/Ignacio to write}  
\item \texttt{step-70}
  \todo[inline]{Also need to update announce and announce-short if this
    makes it into the release.}
\end{itemize}
